The good, the bad, and the ugly

### 2024-10-29 paper/algorithms.tex
update

$ \theta = \{ x \in \mathbb{R} \,|\, \theta_{min} \leq x \leq \theta_{max} \}$: Latent trait levels, where $\theta_{min}$ is the minimum value of $\theta$ and $\theta_{max}$ is its maximum value \add{(non sono sicura della x)}

$||\theta||$: cardinality of the latent trait

@@

\begin{enumerate}
	\item $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$
	\item $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$  \add{ho dei dubbi su questa notazione. la media è calcolata attraverso i valori di theta}. In alternativa a questa notazione: $\overline{\Delta}_{\mathbf{TIF}^{Q}} = \frac{|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|}{||\theta||}$

@@

@@

$D$: Item selected at each iteration

$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D^k\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D^k$

@@

At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,

\begin{enumerate}
	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
	\item $D^k = \arg \min_{i \in B\setminus Q^k} |\theta_{target} - b_i|$
	\item $\mathbf{PIF}_D^k = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
	\end{itemize}
\end{enumerate}

@@

$D$: Item selected at each iteration

$\theta_{target}$: theta target selected at each iteration

$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D$

$||Q^k \cup \{D\}||$: cardinality of $Q^k \cup \{D\}$ at iteration $k$

@@

At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,

\begin{enumerate}
	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
	\item $IIF_{i \in B \setminus Q^k} = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
	\item $D := \arg \min_{i \in B\setminus Q^k} |\theta_{target} - IIF_i|$
	\item $\mathbf{PIF}_{D^k} = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
	\end{itemize}
\end{enumerate}

@@

$D$: provisional item selected at each iteration

@@

At $k =0$, $\mathbf{PIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate

\begin{enumerate}
	\item  $A^k = B \setminus Q^k$ (sets of available items at iteration $k$)
	\item $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$
	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i^k|$
	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$: 
	\begin{itemize}
		\item  If true, $k := k + 1,$ $Q^{k} = Q^{k-1} \cup \{D\}$, restart from 1 \add{C'è il meno 1 per la stessa ragione scritta per ILA e ISA}

>>>>

%$ \theta = \{ x \in \mathbb{R} \,|\, \theta_{min} \leq x \leq \theta_{max} \}$: Latent trait levels, where $\theta_{min}$ is the minimum value of $\theta$ and $\theta_{max}$ is its maximum value \add{(non sono sicura della x)}

%$||\theta||$: cardinality of the latent trait

$||X||$: cardinality of $X$

@@

\begin{enumerate}
	\item $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$, where $||Q||$ is the cardinality of set $Q$
	\item $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$ %, that is the mean across all $\theta$ levels of the absolute difference between $TIF^*$ and $TIF^Q$ %\add{ho dei dubbi su questa notazione. la media è calcolata attraverso i valori di theta}. In alternativa a questa notazione: $\overline{\Delta}_{\mathbf{TIF}^{Q}} = \frac{|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|}{||\theta||}$

@@

\add{spiegazione dell'algoritmo a parole}

@@

$i^*$: Item selected at each iteration

%$\mathbf{pTIF}^k = \frac{\sum_{i\in Q^{k-1} \cup \{i^*\}} IIF_i}{||Q^{k-1}||+1}$, mean tif at iteration $k$, including the item selected in $D$

@@

At $k = 0$: $\mathbf{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,

\begin{enumerate}
	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$
	\item $i^* = \arg \min_{i \in B\setminus Q^{k}} |\theta_{target} - b_i|$
	\item $\mathbf{pTIF}_{i^*} = \frac{TIF^k + IIF_{i^*}}{||Q^{k}|| + 1}$ %$\mathbf{pTIF}_{i^*}= \frac{\sum_{i \in Q^{k} \cup \{i^*\}} IIF_i}{||Q^{k} \cup \{i^*\}||}$ $=$ 
	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{pTIF}_{i^*}| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
		\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF target, hence: 
		$Q_{ILA} = Q^k$
	\end{itemize}
\end{enumerate}

@@

$i^*$: Item selected at each iteration

%$\mathbf{pTIF}^k = \frac{\sum_{i\in Q^{k-1} \cup \{i^*\}} IIF_i}{||Q^{k-1}||+1}$, mean tif at iteration $k$, including the item selected in $D$

@@

At $k = 0$: $\mathbf{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,

\begin{enumerate}
	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
%	\item $IIF_{i \in B \setminus Q^k}(\theta_{target}) = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
	\item $i^* := \arg \max_{i \in B\setminus Q^k} IIF_i(\theta_{target})$
	\item $\mathbf{pTIF}_{i^*} = \frac{TIF^k + IIF_{i^*}}{||Q^{k}|| + 1}$
	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
	\end{itemize}
\end{enumerate}

@@

$i^*$: provisional item selected at each iteration

@@

At $k =0$, $\mathbf{PIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
\alert{gira il cirterio di terminazione e uniforma con gli altri}
\begin{enumerate}
	\item  $A^k = B \setminus Q^k$ (sets of available items at iteration $k$)
	\item $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$
	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i|$
	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item  If true, $k := k + 1,$ $Q^{k} = Q^{k-1} \cup \{D\}$, restart from 1 \add{C'è il meno 1 per la stessa ragione scritta per ILA e ISA}
